FastSRM: A fast, memory efficient and identifiable implementation of the shared response model

### 2021-11-25 paper/main.tex
clean requirements

While brainiak and nilearn are useful to reproduce some of our experiments, they
are not strong dependencies and FastSRM only needs numpy ($\geq 1.12$), scipy
($\geq 0.18.0$), matplotlib ($\geq 2.0.0$), scikit-learn ($geq 0.23),

>>>>

While brainiak and nilearn are useful to reproduce some of our experiments, they
are not strong dependencies and FastSRM only needs numpy ($\geq 1.12$), scipy
($\geq 0.18.0$), matplotlib ($\geq 2.0.0$), scikit-learn ($geq 0.23$), pytest
($\geq 6.2.5$) , joblib ($\geq 1.1.0)
